The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China

### 2019-09-23 Documentation/Response_to_AEJ_Editor.tex

\documentclass[twoside,12pt,leqno]{article}
%\documentclass[twoside,12pt,leqno]{report}

\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,multirow,upgreek}
\usepackage[capposition=bottom]{floatrow} % For Figure Notes
\usepackage{graphicx,pstricks,epstopdf}
\usepackage{url}      % This package helps to typeset urls

%\usepackage{apacite}
%\usepackage{natbib}   % This is a great aid with bibliographies
%\setcitestyle{authoryear,round,semicolon,aysep={},yysep={,},notesep={:}}

\usepackage[title]{appendix}
\renewcommand{\appendixname}{Appendix}

\usepackage[authoryear,comma]{natbib}
\renewcommand{\bibfont}{\small}
\setlength{\bibsep}{0em}

%\usepackage[sc,tiny,center]{titlesec}
\usepackage{titlesec}
\titleformat*{\section}{\sc \center}
\titleformat*{\subsection}{\it \center}
\renewcommand\thesection{\textnormal{{\Roman{section}}}}
\renewcommand{\refname}{Reference}
\usepackage[font={sc,small}]{caption}

\usepackage[%dvipdfmx,%
            bookmarks=true,%
            pdfstartview=FitH,%
            breaklinks=true,%
            colorlinks=true,%
            %allcolors=black,%
            citecolor=blue,
            linkcolor=red,
            pagebackref=true]{hyperref}

\renewcommand{\rmdefault}{ptm}
%\usepackage[lite]{mtpro2}
% use Palatinho-Roman as default font family
%\renewcommand{\rmdefault}{ppl}
\usepackage[scaled=0.88]{helvet}
\makeatletter   % Roman Numbers
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\newcommand{\E}{\mathbb{E}}
\newcommand{\e}{\mathrm{e}}
\DeclareMathOperator*{\argmax}{argmax}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\gvec}[1]{{\boldsymbol{#1}}}

\usepackage[hmargin={1.2in,1.2in},vmargin={1.5in,1.5in}]{geometry}
\usepackage{threeparttable,booktabs,multirow} % This allows notes in tables

\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{CJK}
\usepackage[title]{appendix}
\renewcommand{\appendixname}{Appendix}
\newtheorem{result}{Result}
\setlength{\unitlength}{1mm}

\topmargin -1cm        % read Lamport p.163
\oddsidemargin -0.04cm   % read Lamport p.163
\evensidemargin -0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth 16.59cm
\textheight 21.94cm
\renewcommand\baselinestretch{1.15}
\parskip 0.25em
\parindent 1em
\linespread{1}

% Set header and footer
%\usepackage{fancyhdr}
%\pagestyle{fancy}
%\fancyhead{}
%\fancyhead[LE,RO]{\thepage}
%\cfoot{}
%\renewcommand{\headrulewidth}{0pt}

%\pdfoptionpdfminorversion 6

\begin{document}

\title{\large{THE LETTER TO THE EDITOR}}
\date{}
\maketitle

\vspace{-1.75cm}

\begin{flushleft}
Dear Dr. Moll,
\end{flushleft}

This letter summarizes our responses to the comments that we received from you and the referees after our resubmission to the \textit{American Economic Journal: Macroeconomics}. We truly appreciate it that you have conditionally accepted our paper. Overall, it has been a wonderful experience working with the \textit{AEJ: Macro}. It was very enjoyable revising our paper following the guidance we received from you and the referees.

We have taken the expositional comments from both referees. We have also followed your advice on leaving the CES case in Appendix J. Our responses in detail are as follows.

\begin{flushleft}
\textbf{Response to Referee 1's Comments:}
\end{flushleft}

\begin{enumerate}
    \item
    We thank Referee 1 for mentioning the paper by \citet{Heetal:2019} to us. It is clear that the paper used a different dataset, which has a panel structure. However, since the authors did not provide enough details on the original source of the environmental dataset they used---possibly due to the lack of an official English translation for the name of the dataset---we had a really hard time identifying the exact dataset. Our educated guess is that they were using the firm-level data from \textit{Annual Statistic Report on Environment in China} (in Chinese \begin{CJK}{GBK}{kai}中国环境统计年报\end{CJK}), but we cannot be 100\% sure.

    We talked with our colleagues who have direct access to the above dataset, and learned that there are at least two important differences between that dataset and the one we used. First, the firm-level emission data in the Annual Statistic Report were mostly self-reported by the firms, while the emission data in our dataset were collected by well-trained field staff who could also borrow manpower from local government agencies. As a result, the data quality of the Annual Statistic Report is likely to be lower. \citet{Heetal:2019} seemed to be concerned with the quality of their dataset as well, for which they wrote in their paper that ``Unlike the ASIF, however, we are less confident about the quality of ESR data.'' Second, while the treatment equipment data in our dataset plays a key role in our analysis, the Annual Statistic Report does not provide any information on the treatment equipment used by firms.

    \item
    We have taken Referee 1's advice, removed some footnotes and put some into the main text. We have also removed italics from more than a dozen of words.

    Specifically, the following footnotes from our previous draft are removed: 2, 3, 4, 7, 19, 23, 28, and 41. The following footnotes are integrated into the main text: 10, 12, 22, 25, 36, 39, 44, and 49. We have also merged Footnotes 16 and 17. As a result, the total number of footnotes has been reduced from 52 to 35.

    \item
    In our accounting exercise in Section I.C., we do take the U.S. as a benchmark, since we have data on the U.S. firm size distribution. In our quantitative analysis, however, we are not able to do that, simply because we do not have access to the U.S. firm-level data. Instead, we remove all the correlated distortions from our benchmark model. We did include some discussion on the economic interpretation of the measured wedges that we call distortions in Part \textit{Correlated Distortions} of Section II.A, with Appendix D.1 providing further details. We choose to call these measured wedges as distortions because we prefer to stay close to the literature. In that section, we have cited two survey articles by \citet{RestucciaRogerson:2013, RestucciaRogerson:2017} that elaborate this interpretation issue that the referee concerns. That said, we believe that it is of interest to carry out an additional exercise where the U.S. is the benchmark, if the U.S. firm-level data are available, and we leave this interesting exercise to future work.
\end{enumerate}

\begin{flushleft}
\textbf{Response to Referee 3's Comments:}
\end{flushleft}

\begin{enumerate}[1.]
    \item
    \textit{Introduction}
    \begin{enumerate}[(1)]
        \item
        The sentence has been changed to the following: ``Not only do large firms generate fewer pollutants per output during production, but they are also more likely to use advanced end-of-pipe treatment technologies that require large installation costs.'' Please see the middle of the first paragraph on Page 2 of our new draft.
        \item
        The sentence has been changed as follows: ``Our results show that while the progressiveness of distortions does not imply large output losses, it plays a central role in amplifying aggregate pollution: replacing the progressive taxes with flat taxes would cause a 7\% increase in aggregate output, and a 30\% decrease in aggregate pollution.'' Please see the end of the last paragraph on Page 3 of our new draft.
        \item
        We have removed some footnotes and integrated some into the main text. Specifically, the following footnotes from our previous draft are removed: 2, 3, 4, 7, 19, 23, 28, and 41. The following footnotes are integrated into the main text: 10, 12, 22, 25, 36, 39, 44, and 49. We have also merged Footnotes 16 and 17. As a result, the total number of footnotes has been reduced from 52 to 35.
    \end{enumerate}

    \item
    \textit{Model}
    \begin{enumerate}[(1)]
        \item
        We have explained what the superscripts $c$ and $d$ refer to when they first appear in the model section; please see the beginning of the second paragraph of part \textit{Household} in Section II.A (page 13) of our new draft. Specifically, the superscript $c$ refers to the non-polluting sector, and $d$ refers to the polluting sector.
        \item
        In our initial submission, our model had one sector and two types of treatment technologies, so we used the index $i=0,1$ to denote the type of treatment technology ($i=1$ for clean technology). In our version, there were two sectors in the model, so we used $i=0,1$ to denote the treatment technologies and $i=c,d$ to denote the sectors. It seems that the use of $i$ in both places has caused some confusion, hence we use the index $j=0,1$ in our new draft. We apologize for the confusion. The $j$ superscript is needed though, as there are a few technology-specific variables that we refer to.
    \end{enumerate}

    \item
    \textit{Quantitative Exercises}

    We sincerely appreciate it that Referee 3 finds the results in Appendix J interesting. Indeed, this exercise is inspired by the referee's comments. We considered this suggestion very carefully; however, we decided to leave these results in Appendix J as they are for the following reasons. First, the firm-level data suggest that there are severe correlated distortions in both the polluting and non-polluting sectors. Therefore, we think it is more natural to consider removing distortions from both sectors. Second, when we remove the correlated distortions from the polluting sector only, the results depend critically on the elasticity of substitution between the two sectors $\rho$. Unfortunately, we have not been able to come up with a good estimate of $\rho$ yet. On the other hand, if we remove distortions from both sectors, the value of $\rho$ has very limited impact on the results.
\end{enumerate}

\bibliographystyle{aea}
\bibliography{./Dissertation1}

\end{document}

### 2019-09-23 Documentation/Response_to_Ref1.tex

\documentclass[twoside,12pt,leqno]{article}
%\documentclass[twoside,12pt,leqno]{report}

\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,multirow}
\usepackage[capposition=bottom]{floatrow} % For Figure Notes
\usepackage{graphicx,pstricks,epstopdf}
\usepackage{url}      % This package helps to typeset urls

@@

\begin{document}

\title{\large{RESPONSES TO REFEREE 1'S COMMENTS}}
\date{}
\maketitle

\vspace{-1.75cm}

\begin{flushleft}
To Referee \#1,
\end{flushleft}

This letter summarizes our response to Referee 1’s report, which begins with ``The paper says no existing economic research...'' We thank Referee 1 again for the comments we received. Below, we respond to Referee 1's comments point by point.

### 2019-09-23 Documentation/Pollution_Final_AEJ_Template_Ver2.tex
final submission

% Uncomment the next line to use the natbib package with bibtex
\usepackage{natbib}

@@

\newcommand{\E}{\mathbb{E}}
\newcommand{\e}{\mathrm{e}}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}

@@

\title{The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China}
\shortTitle{FIRM SIZE DISTRIBUTION AND POLLUTION}
\author{Ji Qi, Xin Tang, and Xican Xi\thanks{%
Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and the International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: China Center for Economic Studies, School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433, and  Shanghai Institute of International Finance and Economics (e-mail:xicanxi@fudan.edu.cn). We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward C. Prescott, Diego Restuccia, Todd Schoellman, V. Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees. We also benefited from the comments received at Arizona State University, the Chinese Academy for Environmental Planning, Duke University, the International Monetary Fund, the U.S. International Trade Commission, Peking University, Shanghai University of Finance and Economics, Singapore Management University, Stony Brook University, Washington State University, Wuhan University, and Zhejiang University. We sincerely thank the China Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data. This paper has been screened to ensure that no confidential data are revealed.}}
\date{\today}
\pubMonth{Month}
\pubYear{Year}
\pubVolume{Vol}
\pubIssue{Issue}
\JEL{E23, L11, O44, Q52, Q53, Q56}
\Keywords{Firm Size Distribution, Correlated Distortion, Industrial Water Pollution}

@@

Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the total costs of air and water pollution in China are about 6\% of China's GDP. The health costs of pollution are estimated to be 4\% of GDP in China, the majority of which are associated with premature deaths caused by pollution. See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for reviews of empirical studies on pollution in China.} Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies. An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or largely exacerbated by policy distortions and/or market inefficiencies.

In this paper, we argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China. %\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China. Section I provides more details.}
First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China. %\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD). The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).}  Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs.
Not only do large firms generate  fewer pollutants per output during production, but they are also more likely to use advanced end-of-pipe treatment technologies that require large installation costs. Second, large firms account for a smaller proportion of the total employment in China than in the United States. For the top five polluting industries in China, firms with more than 400 employees account for 20\% of the total employment compared with close to 70\% for the U.S. counterparts. If we take the U.S. economy as a less distorted benchmark, these facts suggest that distortions to firm size distribution could have important environmental consequences in China.

Motivated by these facts, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on \citet{Lucas:1978b} to evaluate how firm-level distortions affect aggregate output and pollution. The model has the following key features. First, firms in each sector differ in their productivity levels. There is a stand-in household with a continuum of members, and each member draws a sector specific managerial ability from a given distribution. When members choose to be manager, they enter the sector their managerial ability belongs to and the ability determines the TFP of the firm they run. Second, firms differ in pollution intensity as well. As in \citet{CopelandTaylor:1994}, pollution emissions are a by-product of production for firms in the polluting sector. Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output. %\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that. Without further data, we model the emissions generated during production in a reduced-form way, which is then calibrated to the data. Section I.B discusses this point in more details.}
Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as clean technology later, after paying a fixed adoption cost. Firms in the polluting sector are subject to environmental regulations such that firms that do not use the clean technology face a penalty that takes away a fraction of their profits. As a result, our model predicts that only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with the fact that large firms are more likely to use clean technology.

Finally, we assume that firms face distortions that increase with their TFP, or \textit{correlated} distortions following the terminology of \citet{RestucciaRogerson:2008}, which are modeled as progressive output taxes.\footnote{\citet{Guneretal:2008} study a closely related type of distortions, namely \textit{size-dependent} distortions, which increase with firm or establishment size (the amount of capital, labor or output). An example is the many labor regulations in Italy, Spain and France that start to bind on firms with more than a certain number of employees. Both correlated and size-dependent distortions lead to a reallocation of resources from high TFP to low TFP firms, and they are essentially equivalent when distortions do not lead to rank reversal defined as more productive firms being smaller [\citet{Hopenhayn:2014}].} We find in our data that firms with higher TFP exhibit substantially higher average products of capital and labor in both the polluting and non-polluting sectors, indicating that more productive firms do face higher distortions [\citet{HsiehKlenow:2009, HsiehKlenow:2014}]. As emphasized by previous studies, such as \citet{RestucciaRogerson:2008} and \citet{HsiehKlenow:2014}, correlated distortions lower both mean firm size and aggregate output, since they limit the operations of productive firms and allow too many unproductive firms to survive and expand. A new insight from our model is that correlated distortions also increase aggregate pollution intensity for two reasons. First, they lower the profits of productive firms which reduces their incentives to adopt the clean technology. Therefore fewer firms adopt clean technology in the equilibrium with correlated distortions. Second, they take production factors away from large productive firms that also have lower pollution intensity, which drives up the average pollution intensity further.

Conventionally, environmental economics decomposes changes in aggregate pollution into three effects: scale (change in aggregate output), composition (reallocation across sectors), and technique (change in sectoral pollution intensity) effects.\footnote{See for example, \citet{GrossmanKrueger:1993}, \citet{CopelandTaylor:2004} and \citet{Levinson:2009} among others.} Our model allows us to assess structurally how distortions affect aggregate pollution through the three channels. Moreover, our model and data allow us to further decompose the technique effect into within sector reallocation across firms and the change in the adoption of clean technology.

To discipline our quantitative analysis, we calibrate our model to match the observed pollution intensity, the adoption of clean technology, the correlation between distortions and firm TFP, and the firm size distribution in the Chinese data. We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector. We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.%\footnote{Here we follow the so-called \textit{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms. Several examples of such policies include size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, poor enforcement of contracts, and internal trade costs, among others. This approach has been widely used in the misallocation literature, for instance, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.}

Our quantitative results show that removing correlated distortions from both sectors would increase mean firm size by 130\% and aggregate output by 30\%, while lowering the pollution intensity of the polluting sector by 42\%. Since both sectors share similar distributions of firm TFP and distortions in the data, eliminating correlated distortions induces little reallocation across sectors. Therefore, aggregate pollution drops by 23\% because the technique effect dominates the scale effect. About half of the technique effect comes from the reallocation of factors across firms, while the rest is from a 27 percentage points increase in the adoption rate of clean technology. To isolate the importance of the progressivity of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant. Our results show that while the progressivity of distortions does not imply large output losses, it plays a central role in amplifying aggregate pollution: replacing the progressive taxes with flat taxes would cause a 7\% increase in aggregate output, and a 30\% decrease in aggregate pollution.

@@

Another line of research focuses on how international trade affects the environment through resource reallocation across heterogeneous firms. \citet{Cherniwchanetal:2017} provide a comprehensive survey of recent contributions.\footnote{Notable examples include \citet{Martin:2013}, \citet{Cherniwchan:2017}, \citet{BarrowsOllivier:2016}, \citet{Forslidetal:2015}, and \citet{ShapiroWalker:2015}. A more detailed comparison between our paper and this line of research can be found in Online Appendix H.} Our paper differs from this literature in two aspects. First, most studies in this literature, with the exception of \citet{ShapiroWalker:2015}, are empirical where models are used primarily to motivate the empirical specification indirectly. Instead, we discipline our general equilibrium model using firm-level data directly in an internally consistent way, and quantitatively assess counterfactual policies using the model. Our quantitative analysis explicitly takes into account the general equilibrium effects of alternative policies, allowing us to investigate novel policy implications that are absent from reduced-form or partial equilibrium analyses. Second, using the firm-level data on treatment technologies, we provide an explanation for the negative correlation between firm size and pollution intensity. It allows us to not only investigate the overall effects of distortions, but also quantify an important channel through which the distortions affect emissions, namely, the adoption of clean technology.

@@

In this section, we describe our empirical findings on the firm-level pollution intensity and the firm size distribution in China. We start by introducing the data sources we use, and then document the key facts on pollution intensity, pollution treatment technologies and employment shares across firms of different sizes. In the end, using a simple accounting exercise, we show that firm size distribution plays a quantitatively important role in aggregate pollution intensity.

@@

This study draws upon three major data sources: the 2007 National General Survey of Pollution Sources (NGSPS) in China, the 2004 China National Economic Census (CNEC), and the Statistics of U.S. Businesses (SUSB).

\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China. %\footnote{A more detailed description of the dataset can be found in Online Appendix A.}
It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for the centralized treatment of pollution. In this study, we focus on the {industrial pollution sources}, which consist of businesses generating pollutants from the 39 manufacturing industries. The survey is organized directly by the State Council with data collection and quality control done by specially trained field staffs. According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)]}, faking data would lead to financial penalties or even lawsuits. Therefore, the dataset is administrative in nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper. Our results will be contaminated only if under-reporting by large firms is more severe than that by small firms, which is less likely in most polluting industries since larger firms are usually inspected more carefully. For instance, many large firms in these industries are identified as \textit{key sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset. See, for example, \citet{Niuetal:2016}, \citet{Qietal:2017} and the references therein. A more detailed description of the dataset can be found in Online Appendix A. %\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}

>>>>

% Uncomment the next line to use the natbib package with bibtex
%\usepackage{natbib}

@@

\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}

@@

\title{The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China}
\shortTitle{FIRM SIZE DISTRIBUTION AND POLLUTION}
\author{Ji Qi, Xin Tang, and Xican Xi\thanks{%
Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (qiji@caep.org.cn); Tang: Center for Economic Development and Research, Economics and Management School, Wuhan University, and International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (zjutangxin@gmail.com); Xi: China Center for Economic Studies, School of Economics, Fudan University, and Shanghai Institute of International Finance and Economics, 600 Guoquan Road, Shanghai, China, 200433 (xicanxi@fudan.edu.cn). We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Dong Cao, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward Prescott, Diego Restuccia, Todd Schoellman, V. Kerry Smith, Gustavo Ventura, Jinnan Wang, Daniel Yi Xu, Fang Yu, the editor and three anonymous referees. We also benefited from the comments received from seminars at many institutions. We thank the Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data. This paper has been screened to ensure that no confidential data are revealed. The results and conclusions in this paper are those of the authors, and do not necessarily reflect the views of the MEE or IMF, its Executive Board, or IMF management. For financial support, Qi acknowledges the National Key R\&D Program of China (2016YFC0207604); and Tang thanks the Key Grant of Ministry of Education of China (16JJD790045).}}
\date{\today}
\pubMonth{Month}
\pubYear{Year}
\pubVolume{Vol}
\pubIssue{Issue}
\JEL{E23, L11, O44, Q52, Q53, Q56}
\Keywords{Firm Size Distribution, Correlated Distortion, Industrial Water Pollution}

@@

Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the total costs of air and water pollution in China are about 6\% of China's GDP. The health costs of pollution are estimated to be 4\% of GDP in China, the majority of which are associated with premature deaths caused by pollution. See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for reviews of empirical studies on pollution in China.} Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies. An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or is it largely exacerbated by policy distortions and/or market inefficiencies.

In this paper, we argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China. First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries (by chemical oxygen demand emissions) in China. Not only do large firms generate  fewer pollutants per output during production, but they are also more likely to use advanced end-of-pipe treatment technologies that require large installation costs. Second, large firms account for a smaller proportion of the total employment in China than in the United States. For the top five polluting industries in China, firms with more than 400 employees account for 20\% of the total employment compared with close to 70\% for the U.S. counterparts. If we take the U.S. economy as a less distorted benchmark, these facts suggest that distortions to firm size distribution could have important environmental consequences in China.

Motivated by these facts, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on \citet{Lucas:1978b} to evaluate how firm-level distortions affect aggregate output and pollution. The model has the following key features. First, firms in each sector differ in their productivity levels. There is a stand-in household with a continuum of members, and each member draws a sector specific managerial ability from a given distribution. When members choose to be manager, they enter the sector their managerial ability belongs to and the ability determines the TFP of the firm they run. Second, firms differ in pollution intensity as well. As in \citet{CopelandTaylor:1994}, pollution emissions are a by-product of production for firms in the polluting sector. Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output. Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as clean technology later, after paying a fixed adoption cost. Firms in the polluting sector are subject to environmental regulations such that firms that do not use clean technology face a penalty that takes away a fraction of their profits. As a result, our model predicts that only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with the fact that large firms are more likely to use clean technology.

Finally, we assume that firms face distortions that increase with their TFP, or \textit{correlated} distortions following the terminology of \citet{RestucciaRogerson:2008}, which are modeled as progressive output taxes.\footnote{\citet{Guneretal:2008} study a closely related type of distortions, namely \textit{size-dependent} distortions, which increase with firm or establishment size (the amount of capital, labor or output). An example is the many labor regulations in Italy, Spain and France that start to bind on firms with more than a certain number of employees. Both correlated and size-dependent distortions lead to a reallocation of resources from high TFP to low TFP firms, and they are essentially equivalent when distortions do not lead to rank reversal defined as more productive firms being smaller [\citet{Hopenhayn:2014}].} We find in our data that firms with higher TFP exhibit substantially higher average products of capital and labor in both the polluting and non-polluting sectors, indicating that more productive firms do face higher distortions [\citet{HsiehKlenow:2009, HsiehKlenow:2014}]. As emphasized by previous studies, such as \citet{RestucciaRogerson:2008} and \citet{HsiehKlenow:2014}, correlated distortions lower both mean firm size and aggregate output, since they limit the operation of productive firms and allow too many unproductive firms to survive and expand. A new insight from our model is that correlated distortions also increase aggregate pollution intensity for two reasons. First, they lower the profits of productive firms which reduce their incentives to adopt the clean technology. Therefore fewer firms adopt clean technology in the equilibrium with correlated distortions. Second, they take production factors away from large productive firms that also have lower pollution intensity, which drives up the average pollution intensity further.

Conventionally, environmental economics decomposes changes in aggregate pollution into three effects: scale (change in aggregate output), composition (reallocation across sectors), and technique (change in sectoral pollution intensity) effects.\footnote{See for example, \citet{GrossmanKrueger:1993}, \citet{CopelandTaylor:2004} and \citet{Levinson:2009} among others.} Our model allows us to assess structurally how distortions affect aggregate pollution through the three channels. Moreover, our model and data allow us to further decompose the technique effect into within sector reallocation across firms and the change caused by the adoption of clean technology.

To discipline our quantitative analysis, we calibrate our model to match the observed pollution intensity, the adoption of clean technology, the correlation between distortions and firm TFP and the firm size distribution in the Chinese data. We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector. We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.

Our quantitative results show that removing correlated distortions from both sectors would increase mean firm size by 130\% and aggregate output by 30\%, while lowering the pollution intensity of the polluting sector by 42\%. Since both sectors share similar distributions of firm TFP and distortions in the data, eliminating correlated distortions induces little reallocation across sectors. Therefore, aggregate pollution drops by 23\% because the technique effect dominates the scale effect. About half of the technique effect comes from the reallocation of factors across firms, while the rest is from a 27 percentage points increase in the adoption rate of clean technology. To isolate the importance of the progressiveness of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant. Our results show that while the progressiveness of distortions does not imply large output losses, it plays a central role in amplifying aggregate pollution: replacing the progressive taxes with flat taxes would cause a 7\% increase in aggregate output, and a 30\% decrease in aggregate pollution.

@@

Another line of research focuses on how international trade affects the environment through resource reallocation across heterogeneous firms. \citet{Cherniwchanetal:2017} provide a comprehensive survey of recent contributions.\footnote{Notable examples include \citet{Martin:2013}, \citet{Cherniwchan:2017}, \citet{BarrowsOllivier:2016}, \citet{Forslidetal:2015} and \citet{ShapiroWalker:2015}. A more detailed comparison between our paper and this line of research can be found in Online Appendix H.} Our paper differs from this literature in two aspects. First, most studies in this literature, with the exception of \citet{ShapiroWalker:2015}, are empirical where models are used primarily to motivate the empirical specification indirectly. Instead, we discipline our general equilibrium model using firm-level data directly in an internally consistent way, and quantitatively assess counterfactual policies using the model. Our quantitative analysis explicitly takes into account the general equilibrium effects of alternative policies, allowing us to investigate novel policy implications that are absent from reduced-form or partial equilibrium analyses. Second, using the firm-level data on treatment technologies, we provide an explanation for the negative correlation between firm size and pollution intensity. It allows us to not only investigate the overall effects of distortions, but also quantify an important channel through which the distortions affect emissions, namely, the adoption of clean technology.

@@

In this section, we describe our empirical findings on the firm-level pollution intensity and the firm size distribution in China. We start by introducing the data sources we use, and then document key facts on pollution intensity, pollution treatment technologies and employment shares across firms of different sizes. In the end, using a simple accounting exercise, we show that firm size distribution plays a quantitatively important role in aggregate pollution intensity.

@@

This study draws upon three major data sources: the 2007 National General Survey of Pollution Sources (NGSPS) of China, the 2004 China National Economic Census (CNEC), and the Statistics of U.S. Businesses (SUSB).

\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China. It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for centralized treatment of pollution. In this study, we focus on the {industrial pollution sources}, which consist of businesses generating pollutants from the 39 manufacturing industries. The survey is organized directly by the State Council with data collection and quality control done by specially trained field staff. According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)]}, faking data would lead to financial penalties or even lawsuits. Therefore, the dataset is administrative in its nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper. Our results will be contaminated only if under-reporting by large firms is more severe than that by small firms, which is less likely in most polluting industries since larger firms are usually inspected more carefully. For instance, many large firms in these industries are identified as \textit{key sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset. See, for example, \citet{Niuetal:2016}, \citet{Qietal:2017} and the references therein. A more detailed description of the dataset can be found in Online Appendix A.

The NGSPS collects information on the emissions of multiple air, water and solid waste pollutants. In this paper, we focus on water pollution mainly because the data are more accurately measured than air pollution.\footnote{After our interview with the field staff, we learned that the difference in data quality was mainly caused by the difference in sampling environment. For water pollution, firms rarely discharge wastewater directly. Instead, the wastewater is first stored in a sedimentation tank to settle heavier solids to the bottom and let lighter materials float. This process creates a stable environment for sampling. For air pollutants, the sampling tube has to be placed in the chimneys, where the environment is much more volatile. Moreover, if firms were to manipulate their instant emissions when the field staff is on-site sampling, the sedimentation process makes it more difficult, since firms would have to clean the tank prior to the on-site visit of the field staff.} Among all the water pollutants, we focus on \textit{chemical oxygen demand} (COD), a major water pollutant that is commonly used to measure water quality. It measures the overall quantity of contaminants that will eventually cause oxygen loss and thus the death of living creatures. We choose COD because a much larger share of firms report positive emissions of COD compared to other pollutants. If we focus on other pollutants, such as hexavalent chromium, we would limit ourselves to a much smaller share of firms that engage in special production processes like leather tanning or pigment manufacturing.\footnote{See Table A.1 in Online Appendix A for the share of firms that report positive emissions for different water pollutants. We would like to stress that many firms do not report emissions of specific pollutants such as cyanidium or chromium simply because they do not use related materials in production. It is not because of under-reporting or other issues related to data quality. In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are usually monitored more closely.} Moreover, COD emissions are typically highly correlated with the emissions of other pollutants when both are positive.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and $\text{NH}_4^+$ is 0.82 and that between COD and BOD is 0.94.}
